\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}

### 2016-04-12 tex/paper.tex
Removed unnecessary f \in F
Changed equations according to Johannes spec

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Set} & \textbf{Elements} & \textbf{Semantics} \\ \hline
        C   & $c_0\dots c_n$                & Containers; folders in the virtual file system\\ \hline
        F   & $f_0\dots f_n$                & Files; files, images, videos\\ \hline
        M   & $m_0\dots m_n$                & Content; Metadata for files\\ \hline
        U   & $u_0\dots u_n$                & Users; registered users in the system\\ \hline
        A   & $A[u_0,c_0]\dots A[u_n, c_n]$ & Access matrix; access rights \\ \hline
    \end{tabular}
\end{center}

@@

\begin{equation}
    \begin{split}
        A[u,c] \Rightarrow & u \text{ can read } c \\
        A[u,c] \land \text{ read-only } \notin c \Rightarrow & u \text{ can write to } c \\
        A[u,c] \land \text{ read-only } \notin c \Rightarrow & u \text{ can delete } c \\
        A[u,c] \land f \in c \centernot\Rightarrow & u \text{ can delete } f 
    \end{split}
\end{equation}

@@

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Action} & \textbf{Semantics} \\ \hline
        u, read(o)            & User u reads object o\\ \hline
        u, write(o)           & User u writes object o\\ \hline
        u, copy(o)            & User u copies object o and the copy gets a new ID\\ \hline
        %u, change(o)          & User u locally changes object o \\ \hline
        u, update(o, o')      & User u globally modifies object o based on object o'\\ \hline
        %u, modify(o', o)      & User u globally modifies object o based on object o'\\ \hline
        u, delete(o)          & User u deletes object o\\ \hline
        u, snapshot(o)        & User u takes a snapshot of object o \\ \hline
    \end{tabular}
\end{center}

@@

%\begin{equation} \label{eq:fileupdate}
%    \begin{split}
%        m' & = u, read(m) \land \\
%        f  & = f \in m' \land \\
%        f' & = u, change(f) \land \\
%        u, & write(f') \land \\
%        u, & modify(f', m) \Implies f \in F \land f' \in F
%    \end{split}
%\end{equation}
%\begin{equation}
%    \begin{split}
%        (F, f \in c) \xrightarrow{update(f', c)} (\{f, f'\} \subset F, f' \in c) 
%    \end{split}
%\end{equation}

\vspace{2em}
\textbf{File Update}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {f \in F \\ [fileId = f.id, parent = c \dots] \in M \\ A[u,c]} 
    {F \cup \{f\} \xrightarrow{u, update(fileId, f'.id)} F \cup \{f, f'\}}
\end{equation}
\vspace{1em}

If a user \textit{u} with access rights to a parent container \textit{c} of content \textit{m},
updates a file reference \textit{f} in content \textit{m}, the original file stays intact.

%\begin{equation} \label{eq:contentupdate}
%    \begin{split}
%        m' & = u, read(m) \land \\
%        m'' & = u, change(m') \land \\
%        m''' & = u, modify(m'', m) \Implies \\
%        m''' & \in M \land m \not \in M
%    \end{split}
%\end{equation}

\vspace{2em}
\textbf{Content Update}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {m \in M \\ m \in c \\ A[u,c]}
    {M \cup \{m\} \xrightarrow{u, update(m, m')} M \cup \{m'\}}
\end{equation}
\vspace{1em}

@@

%\begin{equation} \label{eq:containerupdate}
%    \begin{split}
%        c' & = u, read(c) \land \\
%        c'' & = u, change(c') \land \\
%        c''' & = u, modify(c'', c) \Implies \\
%        c''' & \in C \land c \not \in C
%    \end{split}
%\end{equation}
\vspace{2em}
\textbf{Container Update}
\begin{equation} \label{eq:containerupdate}
    \inferrule
    {c \in C \\ A[u,c]}
    {C \cup \{c\} \xrightarrow{u, update(c, c')} C \cup \{m'\}}
\end{equation}
\vspace{1em}

@@

%\begin{equation} \label{eq:copy}
%    \begin{split}
%        & f' = f \in m \\
%        & m' = u, copy(m) \Implies \\
%        & m' \neq m \land \\
%        & f' \in m' \land f' \in m
%    \end{split}
%\end{equation}
\vspace{2em}
\textbf{Copy}
\begin{equation} \label{eq:copy}
    \inferrule
    {m \in M \\ c \in C \\ m \in c \\ A[u,c]}
    {M \cup \{m\} \xrightarrow{u, copy(m')} M \cup \{m, m'\} \land m.id \neq m'.id}
\end{equation}
\vspace{1em}

If a user \textit{u} with access rights to the parent (source and destination) container \textit{c}
of content \textit{m} copies that content, the new content \textit{m'} is not equal to the old
(because of its new ID), however they both contain the same metadata and refer to the same file.

\vspace{2em}
\textbf{Content Deletion}
\begin{equation} \label{eq:delete}
    \inferrule
    {m \in M \\ f \in F \\ f \in m \\ c \in C \\ m \in c \\ A[u,c]}
    {M \cup \{m\} \land F \cup \{f\} \xrightarrow{u, delete(m)} M \cup \{\} \land F \cup \{f\}}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Snapshot}
\begin{equation} \label{eq:snapshot}
    \begin{split}
        [C', M'] := snapshot(tree) & \Implies \\
        \forall c \in tree, copy(c) \in & C' \\
        \forall m \in tree, copy(m) \in & M' \\
        \forall f \in tree, f \in & F
    \end{split}
\end{equation}

@@

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {c \in C \\ A[u,c]}
    {M, C \xrightarrow{[C', M'] := u, snapshot(c)} M \cup M',  C \cup C'}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.

%\begin{equation} \label{eq:delete}
%    \begin{split}
%        f' = f \in (u, read(c)),  \\
%        u, delete(c) \Implies \\
%        c \not \in C \land f' \in F
%    \end{split}
%\end{equation}

@@

\fix Picture of the newest front-end
\begin{figure}[H] 
    \centering{
        \includegraphics[scale=0.4]{frontend.png}
    }
    \caption{Front-end~\cite{BTRFS}}
    \label{fig:frontend}
\end{figure}

>>>>

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Set} & \textbf{Elements} & \textbf{Semantics} \\ \hline
        C   & $c_0\dots c_n$                & Containers; folders in the virtual file system\\ \hline
        F   & $f_0\dots f_n$                & Files; files, images, videos\\ \hline
        M   & $m_0\dots m_n$                & Content; Metadata for files\\ \hline
        U   & $u_0\dots u_n$                & Users; registered users in the system\\ \hline
        A   & $A[u_0,c_0]\dots A[u_n, c_n]$ & Boolean Access matrix; access rights \\ \hline
    \end{tabular}
\end{center}

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Set} & \textbf{Relation} & \textbf{Type} \\ \hline
        \textbf{C} & $\textbf{C} \supseteq C \ni c$ & $\textbf{C}=P_{fin}(P_{fin}(C \cup M))$\\ \hline
        \textbf{M} & $\textbf{M} \supseteq M \ni m$ & $\textbf{M}=P_{fin}(M)$\\ \hline
        \textbf{F} & $\textbf{F} \supseteq F \ni f$ & $\textbf{F}=P_{fin}(F)$\\ \hline
    \end{tabular}
\end{center}

The bold notation (\textbf{C}, \textbf{M}, \textbf{F}) refers to the sets containing all possible
members of that type.

\begin{center}
    \begin{tabular}{ | l | l | p{5cm} |}
        \hline
        \textbf{Element} & \textbf{Type} \\ \hline
        c & $C \cup M$ \\ \hline
        m & $\{id: GUID, file: f\}$ \\ \hline
        f & File \\ \hline
    \end{tabular}
\end{center}

@@

\begin{equation}
    \begin{split}
        A[u,c] \Rightarrow & u \text{ can read } c \\
        A[u,c] \land \neg \text{ read-only(c) } \Rightarrow & u \text{ can write to } c \\
        A[u,c] \land \neg \text{ read-only(c) } \Rightarrow & u \text{ can delete } c \\
        A[u,c] \land f \in c \centernot\Rightarrow & u \text{ can delete } f 
    \end{split}
\end{equation}

@@

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Action} & \textbf{Semantics} \\ \hline
        u, read(m, f)    & User \textit{u} reads \textit{f} from \textit{m}\\ \hline
        u, create(m, c)  & User \textit{u} creates \textit{m} in \textit{c}\\ \hline
        u, update(m, f)  & User \textit{u} updates \textit{f} with \textit{m}\\ \hline
        u, delete(o)     & User \textit{u} deletes \textit{o}\\ \hline
        u, snapshot(o)   & User \textit{u} takes a snapshot of \textit{o} \\ \hline
    \end{tabular}
\end{center}

@@

\vspace{2em}
\textbf{File Read}
\vspace{1em}
\begin{equation} \label{eq:fileread}
    \inferrule
    {(\textbf{*}) \\ C \ni c \ni m \\ A[u,c]} 
    {(C, F) \xrightarrow{u, read(m,f)} (C, F)}
\end{equation}
\vspace{1em}

A user \textit{u} with access rights to a parent container \textit{c} of content \textit{m}
can read a file \textit{f} in content \textit{m}.

These predicates are used in several places and are therefore named \textit{*}.

\vspace{2em}
\textbf{File Creation}
\vspace{1em}
\begin{equation} \label{eq:filecreate}
    \inferrule
    {C \ni c \\ A[u,c] \\ m \centernot \in c \\ \neg readOnly(c)} 
    {(C \cup \{c'\}, F) \xrightarrow{u, create(m,c)} (C \cup \{c \cup \{m\}\}, F \cup \{m.file\})}
\end{equation}
\vspace{1em}

A user \textit{u} with access rights to a non-readonly container \textit{c} can create a content
\textit{m}, containing a file \textit{f}, in container \textit{c}.

\vspace{2em}
\textbf{File Update}
\vspace{1em}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {\textbf{*} \\ c' = c \cup \{m'\} \\ m' = \{id = m.id, file = f'\} \\ \neg readOnly(c)} 
    {(C \cup \{c \cup \{m\}\} , F) \xrightarrow{u, update(m, f')} (C \cup \{c \cup \{m'\}\}, F
    \cup \{f'\}))}
\end{equation}
\vspace{1em}

If a user \textit{u} with access rights to a parent container \textit{c} (which is not read only) of
content \textit{m}, updates a file \textit{f} in content \textit{m}, the original file stays
intact as an effect of Copy-on-Write.

\vspace{2em}
\textbf{File Deletion}
\newline

Files can not be deleted by any user, however all the references to the file can
be deleted, see Consequence \ref{eq:delete}.

\vspace{2em}
\textbf{Content Update}
\vspace{1em}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C \cup \{c \cup \{m\}\}, F) \xrightarrow{u, update(m, m')} ((C \cup \{c \cup \{m'\}\}, F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Container Update}
\vspace{1em}
\begin{equation} \label{eq:containerupdate}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C \cup \{c\}, F) \xrightarrow{u, update(c, c')} (C \cup \{c'\}, F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Copy}
\vspace{1em}
\begin{equation} \label{eq:copy}
    \inferrule
    {\textbf{*} \\ m' = \{id = \text{"fresh"}, file = m.file\} \\ \neg readOnly(c)}
    {(C \cup \{c \cup \{m\}\}, F) \xrightarrow{u, create(c, m')} (C \cup \{c \cup \{m, m'\}\}, F)}
\end{equation}
\vspace{1em}

If a user \textit{u} with access rights to the parent (source and destination) container \textit{c}
of content \textit{m} copies that content, the new content \textit{m'} is not equal to the old
(because of its new ID), however they both contain the same file.

\vspace{2em}
\textbf{Content Deletion}
\vspace{1em}
\begin{equation} \label{eq:delete}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C \cup \{m\}, F) \xrightarrow{u, delete(m)} (C, F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Snapshot}
\vspace{1em}
\begin{equation} \label{eq:snapshot}
    \begin{split}
        [C', M'] := snapshot(tree) & \Implies \\
        \forall c \in tree, copy(c) \in & C' \\
        \forall m \in tree, copy(m) \in & M' \\
        \forall f \in tree, f \in & F
    \end{split}
\end{equation}

@@

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C, F) \xrightarrow{[C', M'] := u, snapshot(c)} (C \cup C' \cup M', F)}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.

@@

\begin{figure}[H] 
    \centering{
        \includegraphics[scale=0.35]{frontend.png}
    }
    \caption{Front-end~\cite{BTRFS}}
    \label{fig:frontend}
\end{figure}
